### 2021-02-25 yfcc100m/paper/vldb2021/design.tex
Expand on API on design section

Listing~\ref{findimagegeo} shows a sample query.
In this particular example, the transaction retrieves
all the images of \textit{alligators}
with probability higher than 0.66,
filter by latitude and longitude within 1 degree,
apply a resize operation to make the images 224x224,
rotate the images 45.34 degrees,
and return the images as "png" files.
It is important to note how the API natively supports basic building
blocks of visual data processing, like resize, rotation, or transcoding
(changing output formats and encodings).
The API allows interaction with metadata, images, videos,
and feature vectors in a similar fashion, and it is fully
documented on the project's Github
wiki~\footnote{https://github.com/IntelLabs/vdms/wiki/API-Description}.

>>>>

Listing~\ref{addimageandautotag} shows a sample query for inserting an image
and its associated metadata to VDMS.
In this example, the transaction inserts an application-defined "Entity" of
the class "autotag", with the "name" property being \textit{alligator},
inserts an Image with its "latitude" and "longitude",
stores the image  as a JPG (VDMS will transcode if needed),
and creates a connection between the Image and the Entity, with a "prob"
property (which indicates the probability of that image
containing an object of type  \textit{alligator}) with a specific value.
Note that no schema needs to be defined in advance.
The Entity of class "autotag", with its properties, are declared and added
at insertion time, without any need to define a schema of objects
(and its properties) before hand.

\begin{listing}[ht!]
\begin{minted}[frame=single,
              framesep=3mm,
              linenos=true,
              xleftmargin=21pt,
              tabsize=4]{js}
"AddEntity"{
    "_ref" : 1,
    "class": "autotag",
    "properties": {
        "name": "alligator"
    }
},
"AddImage":{
    "_ref": 2,
    "properties": {
        "latitude":  36.23433,
        "longitude": -116.80666
    },
    "format": "jpg"
}
"AddConnection": {
    "ref1": 1,
    "ref2": 2,
    "properties": {
        "prob": 0.7653
    }
}

\end{minted}
\caption{Sample Query for Image Insertion -
The query expresses the following:
Insert an Entity of the class "autotag", with the "name" property being
\textit{alligator}, insert an Image with its "latitude" and "longitude",
store the image  as a JPG, and create a connection between
the image and the "autotag",  with a property "prob"
(which indicates the probability of that image
containing an object of type  \textit{alligator}).}
\label{addimageandautotag}
\end{listing}

Listing~\ref{findimagegeo} shows another sample query, in this case, for retrieval.
In this particular example, the transaction retrieves all the images
of \textit{alligators} with probability higher than 0.66,
filter by latitude and longitude within 1 degree,
apply a resize operation to make the images 224x224,
rotate the images 45.34 degrees, and return the images as "png" files.
It is important to note how the API natively supports basic building
blocks of visual data processing, like resize, rotation, or transcoding
(changing output formats and encodings).
The API allows interaction with metadata, images, videos,
and feature vectors in a similar fashion, and it is fully
documented on the project's Github
wiki~\footnote{https://github.com/IntelLabs/vdms/wiki/API-Description}.
